---
title: "Demonstrating the imputeTestBench package"
author: "Mayank"
output:
  html_document
---
#### Introduction

I will demonstrate the use of `imputeTestbench` on dataset nottem which contains monthly average air temperatures measured at Nottingham Castle from 1920 to 1939. This demonstration tries to use maximum functions available in the package.

```{r}
knitr::opts_chunk$set(echo=TRUE)

#load required packages
library(imputeTestbench)
library(ggplot2)

#loading Data
data("nottem")
nottem_ts <- as.ts(nottem)

autoplot(nottem_ts) + ggtitle("Time Series Data")
```

#### Using imputeTestBench for simulating missing value and applying impute methods

```{r}
#Applying imputation using
nottem_ts_imputed <- impute_errors(dataIn = nottem_ts,
  smps = "mcar",
  methods = c("na.approx",
"na.interp", "na_interpolation", "na.locf", "na_mean"),
  errorParameter = "rmse",
  repetition = 10)
print(nottem_ts_imputed)
```
#### Visualization of Errors

```{r plot-errors}

plot_errors(nottem_ts_imputed, plotType = "line")

```

#### Visualization of Imputed Data

```{r plot-impute}
plot_impute(dataIn = nottem_ts, smps = "mcar", showmiss = TRUE)
```

#### Conclusion
This analysis demonstrates the effectiveness of different imputation methods on missing time series data
